---
title: "Hypothesis Testing"
author: "Zhidong Chen"
output: pdf_document
fontsize: 11pt
geometry: margin=1in
header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering \emph}
- \usepackage{xfrac}
---

```{r setup, include = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  Setup

```{r, message = FALSE, echo = TRUE}

# Read data
lawsch85 <- read.csv("data/LAWSCH85.csv")

# Load packages
library(car)
```

# Linear Hypothesis Testing

## 1. Single parameter T-test and Joint Significance F-test

```{r, message = FALSE, echo = TRUE}

# See what variables we have in the data
names(lawsch85)

# Run full unrestricted linear model
model.ur <- lm(lsalary ~ LSAT + 
                       GPA  + 
                       lcost + 
                       rank, 
               data = lawsch85)

# Pull a summary of the model resutls
summary(model.ur) 
```

Single coefficent T-test and F-test of Joint significance of all slope 
parameters are included in the results of summary function


## 2.Test linear combination of parameters

### ~ Method 1:  Use "car::linearHypothesis()"

```{r}
# Examples of different linear hypothesis testing
linearHypothesis(model.ur, c("LSAT = 0", "GPA = 0")) 
# or lht(model.ur, c("LSAT = 0", "GPA = 0"))
linearHypothesis(model.ur, "LSAT + GPA = 0", test = "F")
linearHypothesis(model.ur, "2*LSAT + 1*GPA = 0")
linearHypothesis(model.ur, "2*LSAT + 1*GPA - rank= 0")
```

### ~ Method 2: Run restricted model, then use "anova(model.ur, model.r)"

```{r}
model.r1 <- lm(lsalary ~ llibvol + lcost + rank, data = lawsch85)

# If you we use "anova(model.ur, model.r1)" directly, we get error message:
# Error in anova.lmlist(object, ...) : 
# models were not all fitted to the same size of dataset

# To correct for the error, we need to remove the missing values.
# Missing values are coded as "NA" in R.
# is.na(object) tests weather each item of the "object" has a missing value. 
# It returns logical values, "TRUE" or "FALSE". 
# "!" in front of is.na(object) is the negate sign. 

```
#### Solution:

```{r}
# Remove missing values of GPA and LSAT
lawsch85.subset <- lawsch85[!is.na(lawsch85$GPA) & !is.na(lawsch85$LSAT), ] 

# Unrestricted linear model
model.ur2 <- lm(lsalary ~ LSAT +
                       GPA +
                       llibvol +
                       lcost +
                       rank, 
               data = lawsch85.subset)

# Restricted linear Model
model.r2 <- lm(lsalary ~ llibvol +
                       lcost +
                       rank,
               data = lawsch85.subset)

# Hypothesis testing using F-test
anova(model.ur2, model.r2)
```

#### A note about "car::lht()":

In function lht(), the default test type is an asymptotic Chi-square test. When the model we put in is a lm model such as in all the above examples, the default test type changes 
to F-test automatically. 

**Caution!** When the model we put in is a different type of model, such as the felm 
model, to conduct a F-test, we add an option to your function: test = "F".

```{r}
# For illurstration
linearHypothesis(model.ur2, c("LSAT = 0", "GPA = 0"), test="F") 
```

## 3.Recover F-statistic using regression results

F-statistic formula using Sum of Squared Residuals:SSR
\begin{equation*}
F = \frac{\sfrac{(SSR_r - SSR_{ur})}{q}}{\sfrac{SSR_{ur}}{(n-k-1)}}
\end{equation*}

     Plug in the values from above regressions:
\begin{align*}
F &= \frac{\sfrac{(1.8942 - 1.6427)}{2}}{\sfrac{1.6427}{130}} \\
  &= 9.951604
\end{align*}


